Democracy, Public Support, and Measurement Uncertainty

### 2021-06-06 paper/dcpo_demsupport.Rmd
change theta, theta_aut and theta_dem to SupDem_trim, theta_aut_trim, and theta_dem_trim. @sammo3182

ls_iv <- c("plm::lag(theta, 1)", 
    "plm::lag(theta_dem, 1) + plm::lag(theta_aut, 1) ")

@@

```{r dcpo-modelAJPS}
ls_iv <- c("plm::lag(theta, 1)", 
    "plm::lag(theta_dem, 1) + plm::lag(theta_aut, 1) ")

>>>>

#ls_iv <- c("plm::lag(theta, 1)", 
#    "plm::lag(theta_dem, 1) + plm::lag(theta_aut, 1) ")

ls_iv <- c("plm::lag(SupDem_trim, 1)", 
    "plm::lag(theta_dem_trim, 1) + plm::lag(theta_aut_trim, 1) ") #use trimmed data

@@

```{r dcpo-modelAJPS}
#ls_iv <- c("plm::lag(theta, 1)", 
#    "plm::lag(theta_dem, 1) + plm::lag(theta_aut, 1) ")

ls_iv <- c("plm::lag(theta_trim, 1)", 
    "plm::lag(theta_dem_trim, 1) + plm::lag(theta_aut_trim, 1) ") #use trimmed data
